### 2015-03-10 paper/paper.tex
Include two new weeks in 2015

\begin{figure}[tb]
\caption{Number of weekly matches of word stem ``automat" in US patents, 1976-2015}
	\centering
	\includegraphics[trim=1cm 0cm 0cm 0cm, clip=true, totalheight=0.38\textheight]{./figures/keyword_matches_weekly_1976-2015.pdf}
	\floatfoot{\textit{Note:} Every data point displays sum of matches from searching through one file of weekly patent grant texts; total identified patents: 5.5 mio.; total number of keyword matches: 6.9 mio.\\[0.1cm]
	\textit{Source:} USPTO, Google and own calculations.}
	\label{fig:keyword_match_over_time}
\end{figure}

@@

\begin{figure}[tb]
\caption{Number of identified patents, 1976-2014}
	\includegraphics[trim=0cm 0cm 1cm 0.5cm, clip=true, totalheight=0.25\textheight]{./figures/barchart_identified_patents_1976-2014.pdf}
	\label{fig:summary_stats}
	\floatfoot{\textit{Note:} Identified patents are those found through the search algorithm; the bottom darker-shade bars are the number of distinct patents with at least one match \\[0.1cm]
	\textit{Source:} USPTO, Google and own calculations.}
\end{figure}

@@

\begin{figure}[tb]
\caption{Weekly averages of number of average matches per patent, 1976-2015}
	\centering
	\includegraphics[trim=1cm 0cm 1cm 0cm, clip=true, totalheight=0.4\textheight]{./figures/match_over_nrpatents_weekly_1976-2015.pdf}
	\floatfoot{\textit{Note:} Every data point displays sum of matches from searching through one file of weekly patent grant texts divided by the number of identified patents for that week; the solid line is the HP-filtered trend with $\lambda = 100'000$; the size of markers corresponds to number of patents in week.\\[0.1cm]
	\textit{Source:} USPTO, Google and own calculations.}
	\label{fig:match_per_nrpatents}
\end{figure}

>>>>

\begin{figure}[tb]
\caption{Number of weekly matches of word stem ``automat" in US patents, 1976-2015}
	\centering
	\includegraphics[trim=1cm 0cm 0cm 0cm, clip=true, totalheight=0.38\textheight]{./figures/keyword_matches_weekly_1976-2015.pdf}
	\floatfoot{
	\begin{minipage}{0.8\textwidth}
	\textit{Note:} Every data point displays sum of matches from searching through one file of weekly patent grant texts; total identified patents: 5.5 mio.; total number of keyword matches: 6.9 mio.\\[0.1cm]
	\textit{Source:} USPTO, Google and own calculations.
	\end{minipage}
	}
	\label{fig:keyword_match_over_time}
\end{figure}

@@

\begin{figure}[tb]
\caption{Number of identified patents, 1976-2014}
	\includegraphics[trim=0cm 0cm 1cm 0.5cm, clip=true, totalheight=0.25\textheight]{./figures/barchart_identified_patents_1976-2014.pdf}
	\label{fig:summary_stats}
	\floatfoot{
	\begin{minipage}{0.8\textwidth}
\textit{Note:} Identified patents are those found through the search algorithm; the bottom darker-shade bars are the number of distinct patents with at least one match \\[0.1cm]
	\textit{Source:} USPTO, Google and own calculations. 
	\end{minipage}
		}
\end{figure}

%\begin{figure}[tb]
%\caption{Number of identified patents, 1976-2014}
%	\includegraphics[trim=0cm 0cm 1cm 0.5cm, clip=true, totalheight=0.25\textheight]{./figures/barchart_identified_patents_1976-2014.pdf}
%	\label{fig:summary_stats}
%	\floatfoot{\textit{Note:} Identified patents are those found through the search algorithm; the bottom darker-shade bars are the number of distinct patents with at least one match \\[0.1cm]
%	\textit{Source:} USPTO, Google and own calculations.}
%\end{figure}

@@

\begin{figure}[tb]
\caption{Weekly averages of number of average matches per patent, 1976-2015}
	\centering
	\includegraphics[trim=1cm 0cm 1cm 0cm, clip=true, totalheight=0.4\textheight]{./figures/match_over_nrpatents_weekly_1976-2015.pdf}
	\floatfoot{
	\begin{minipage}{0.8\textwidth}
	\textit{Note:} Every data point displays sum of matches from searching through one file of weekly patent grant texts divided by the number of identified patents for that week; the solid line is the HP-filtered trend with $\lambda = 100'000$; the size of markers corresponds to number of patents in week.\\[0.1cm]
	\textit{Source:} USPTO, Google and own calculations.
	\end{minipage}
	}
	\label{fig:match_per_nrpatents}
\end{figure}
